Exploratory data analysis

### 2021-10-18 slides/data_checking.Rmd
even more cleaning for mariam mtg today

```{r}
j_exp %>% 
  ggplot(aes(x = j_score)) +
  geom_histogram(binwidth = .05) +
  geom_vline(xintercept = 0.7, linetype = "dotted")
```

@@

```{r}
j_exp %>% 
  mutate(subj_num = factor(subj_num)) %>% 
  left_join(q_google_demos, by = "subj_num") %>% 
  ggplot(aes(x = j_score, fill = gender)) +
  geom_histogram(binwidth = .05, position = "identity", alpha = 0.5) +
  geom_vline(xintercept = 0.7, linetype = "dotted")
```

@@

```{r}
j_exp %>% 
  mutate(subj_num = factor(subj_num)) %>% 
  left_join(q_google_demos, by = "subj_num") %>% 
  ggplot(aes(x = age, y = j_score)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_hline(yintercept = 0.7, linetype = "dotted")
```

@@

```{r}
j_recall %>% 
  ggplot(aes(x = rt_end_recall, y = as.integer(acc_recall), color = j_score, fill = j_score)) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), se = FALSE) + 
  scale_color_viridis_c() +
  scale_fill_viridis_c() +
  labs(x = "Recall submit RT", y = "Recall accuracy (strict)", color = "Expertise score", fill = "Expertise score") +
  theme_bw()
```

### Better experts tend to respond faster

Again, this is consistent with an across-participants tendency to respond faster for subsequently correct answers. Better experts who are giving more correct answers are thus more likely to have shorter RTs.

```{r}
j_recall %>% 
  group_by(subj_num, j_score) %>% 
  summarize(rt_q500 = median(rt_end_recall, na.rm = TRUE),
            rt_q250 = quantile(rt_end_recall, .25, na.rm = TRUE),
            rt_q750 = quantile(rt_end_recall, .75, na.rm = TRUE),
            rt_q025 = quantile(rt_end_recall, .025, na.rm = TRUE),
            rt_q975 = quantile(rt_end_recall, .975, na.rm = TRUE),
            rt_mean = mean(rt_end_recall, na.rm = TRUE),
            rt_sd = sd(rt_end_recall, na.rm = TRUE)) %>% 
  ggplot(aes(x = subj_num, y = rt_mean, color = j_score)) +
  geom_errorbar(aes(ymin = rt_mean - rt_sd/2, ymax = rt_mean + rt_sd/2), width = 0, size = 1) +
  geom_point(size = 3) +
  coord_flip() +
  scale_color_viridis_c() +
  theme_bw() +
  theme(axis.text.y = element_blank())
```

```{r}
j_recall %>% 
  ggplot(aes(x = rt_end_recall, y = resp_conf, color = j_score, fill = j_score)) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth(aes(group = subj_num), method = "lm", alpha = 0.05) + 
  scale_color_viridis_c() +
  scale_fill_viridis_c() +
  labs(x = "Recall submit RT", y = "Recall confidence", color = "Expertise score", fill = "Expertise score") +
  theme_bw()
```

@@

```{r}
j_meta %>%
  filter(!is.na(resp)) %>% 
  left_join(j_recall %>% select(subj_num, answer, acc_recall)) %>% 
  mutate(acc_recall = recode(as.character(acc_recall),
                             `FALSE` = "incorrect",
                             `TRUE` = "correct")) %>% 
  ggplot(aes(x = subj_num, fill = resp)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(angle = 30)) +
  facet_grid(~acc_recall) +
  labs(x = "Participant", y = "# facts labeled with that memory state", fill = "Memory state") +
  theme_bw()
```

@@

```{r}
j_meta %>%
  left_join(j_recall %>% select(subj_num, answer, acc_recall)) %>% 
  mutate(acc_recall = recode(as.character(acc_recall),
                             `FALSE` = "incorrect",
                             `TRUE` = "correct")) %>% 
  count(subj_num, acc_recall, resp) %>% 
  group_by(subj_num, acc_recall) %>% 
  mutate(prob = n / sum(n)) %>% 
  ggplot(aes(x = subj_num, y = prob, fill = resp)) +
  geom_col() +
  scale_x_discrete(guide = guide_axis(angle = 30)) +
  facet_grid(~acc_recall) +
  labs(x = "Participant", y = "Percent facts labeled with that memory state", fill = "Memory state") +
  theme_bw()
```

### Metamemory descriptions: Guess

```{r, results = "asis"}
j_meta_desc %>%
  filter(question == "Guess") %>% 
  arrange(subj_num) %>% 
  pull(resp) %>% 
  paste0(">", .) %>% 
  cat(sep = "\n\n")
```

### Metamemory descriptions: Just Know

```{r, results = "asis"}
j_meta_desc %>%
  filter(question == "Just Know") %>% 
  arrange(subj_num) %>% 
  pull(resp) %>% 
  paste0(">", .) %>% 
  cat(sep = "\n\n")
```

### Metamemory descriptions: Related Memory

```{r, results = "asis"}
j_meta_desc %>%
  filter(question == "Related Memory") %>% 
  arrange(subj_num) %>% 
  pull(resp) %>% 
  paste0(">", .) %>% 
  cat(sep = "\n\n")
```

### Metamemory descriptions: Learning Memory

```{r, results = "asis"}
j_meta_desc %>%
  filter(question == "Learning Memory") %>% 
  arrange(subj_num) %>% 
  pull(resp) %>% 
  paste0(">", .) %>% 
  cat(sep = "\n\n")
```

@@

```{r}
encoding %>% 
  ggplot(aes(x = resp, fill = category)) +
  geom_histogram(position = "identity", binwidth = 5, alpha = 0.5)
```

@@

```{r}
encoding %>% 
  ggplot(aes(x = j_score, y = resp, color = category, fill = category)) +
  geom_jitter(alpha = 0.5) +
  geom_smooth(formula = y ~ x, method = "lm")
```

@@

```{r}
encoding %>% 
  ggplot(aes(x = resp, y = rt, color = j_score, fill = j_score)) +
  geom_point() +
  geom_smooth(aes(group = subj_num), method = "lm", se = FALSE) +
  scale_colour_viridis_c() +
  scale_fill_viridis_c()
```

@@

```{r}
encoding %>% 
  mutate(already_knew = fct_relevel(already_knew, "none", "some")) %>% 
  ggplot(aes(x = subj_num, fill = already_knew)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(angle = 30)) +
  labs(x = "Participant", y = "# facts already knew", fill = "Prior knowledge") +
  theme_bw()
```

@@

```{r}
retrieval %>% 
  ggplot(aes(x = retrieval_trial_num, y = acc_recall)) +
  geom_rect(aes(x = NULL, y = NULL, xmin = xmin, xmax = xmax, fill = retrieval_block_type),
            data = retrieval %>%
              select(subj_num, retrieval_block, retrieval_trial_num, retrieval_block_type) %>%
              group_by(subj_num, retrieval_block) %>%
              filter(retrieval_trial_num %in% range(retrieval_trial_num)) %>%
              mutate(xtype = if_else(retrieval_trial_num == min(retrieval_trial_num), "xmin", "xmax")) %>%
              ungroup() %>%
              pivot_wider(names_from = xtype, values_from = retrieval_trial_num) %>% 
              mutate(xmin = xmin - 0.5,
                     xmax = xmax + 0.5),
            ymin = 0, ymax = 1, alpha = 0.5) +
  geom_line() +
  geom_point(aes(color = already_knew)) +
  # scale_colour_viridis_b() +
  scale_y_continuous(n.breaks = 3) +
  facet_grid(subj_num ~ .) +
  labs(x = "Fact recall trial (beginning to end)", y = "Fact recall accuracy", fill = "Chunk type") +
  theme_bw()
```

@@

### Fact recall by already knew status

```{r}
retrieval %>% 
  mutate(acc_recall = if_else(acc_recall > 0, 1, 0)) %>% 
  filter(!is.na(already_knew)) %>% 
  ggplot(aes(x = subj_num, fill = factor(acc_recall))) +
  geom_bar() +
  facet_grid(~already_knew)
```

```{r}
retrieval %>% 
  mutate(acc_recall = if_else(acc_recall > 0, 1, 0)) %>% 
  filter(!is.na(already_knew)) %>% 
  count(subj_num, acc_recall, already_knew) %>% 
  group_by(subj_num, already_knew) %>% 
  mutate(prob = n / sum(n)) %>% 
  ggplot(aes(x = subj_num, y = prob, fill = factor(acc_recall))) +
  geom_col() +
  facet_grid(~already_knew)
```

### Fact recall by ENCODING question order

```{r}
retrieval %>% 
  nest(data = -subj_num) %>% 
  sample_n(10) %>% 
  unnest(data) %>% 
  mutate(encoding_trial_num = if_else(group == "academic", group_trial_num * 2 - 1, group_trial_num * 2)) %>% 
  ggplot(aes(x = retrieval_trial_num, y = acc_recall)) +
  geom_line() +
  geom_point(aes(color = already_knew)) +
  # scale_colour_viridis_b() +
  scale_y_continuous(n.breaks = 3) +
  facet_grid(subj_num ~ .) +
  labs(x = "Encoding trial (beginning to end)", y = "Subsequent fact recall accuracy") +
  theme_bw()
```

@@

Current setup: A-A' 2AFC with similar lure

```{r}
r_pics %>%
  ggplot(aes(x = factor(subj_num), y = resp, color = j_score)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_boxplot() +
  scale_colour_viridis_c() +
  guides(color = FALSE) +
  labs(x = "Participant", y = "Accuracy with confidence (positive = correct)") +
  theme_bw()
```

@@

```{r}
r_source %>%
  ggplot(aes(x = factor(subj_num), y = resp, color = j_score)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_boxplot() +
  scale_colour_viridis_c() +
  guides(color = FALSE) +
  labs(x = "Participant", y = "Accuracy with confidence (positive = correct)") +
  theme_bw()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
  ggplot(aes(x = resp_pic, y = acc_recall, color = j_score, fill = j_score)) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), alpha = 0.02) + 
  scale_color_viridis_c() +
  scale_fill_viridis_c() +
  # facet_grid(~already_knew) +
  labs(x = "Photo recognition accuracy", y = "Fact recall accuracy (generous)") +
  theme_bw()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
  ggplot(aes(x = resp_pic, y = acc_recall, color = cut_number(j_score, 3), fill = cut_number(j_score, 3))) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth( method = "glm", method.args = list(family = "binomial"), alpha = 0.2) + 
  labs(x = "Photo recognition accuracy", y = "Fact recall accuracy (generous)") +
  theme_bw()
```

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         resp_pic = resp_pic / 100,
         j_score = j_score - 0.5) %>% 
  lme4::glmer(acc_recall ~ resp_pic * j_score + (1 | subj_num), data = ., family = "binomial") %>% 
  summary()
```

@@

```{r}
retrieval %>% 
  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
  ggplot(aes(x = resp_source, y = acc_recall, color = j_score, fill = j_score)) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), alpha = 0.05) + 
  scale_color_viridis_c() +
  scale_fill_viridis_c() +
  labs(x = "Source recognition accuracy", y = "Fact recall accuracy (generous)") +
  theme_bw()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall),
         j_score_binary = j_score > 0.72) %>%
  ggplot(aes(x = resp_source, y = acc_recall, color = cut_number(j_score, 4), fill = cut_number(j_score, 4))) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth( method = "glm", method.args = list(family = "binomial"), alpha = 0.2) + 
  labs(x = "Source recognition accuracy", y = "Fact recall accuracy (generous)") +
  theme_bw()
```

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         resp_source = resp_source / 100,
         j_score = j_score - 0.5) %>% 
  lme4::glmer(acc_recall ~ resp_source * j_score + (1 | subj_num), data = ., family = "binomial") %>% 
  summary()
```

@@

```{r}
retrieval %>% 
  ggplot(aes(x = resp_source, y = resp_pic, color = j_score, fill = j_score)) + 
  geom_point(alpha = 0.3) + 
  geom_smooth(aes(group = subj_num), method = "lm", se = FALSE) + 
  scale_color_viridis_c() +
  scale_fill_viridis_c() +
  labs(x = "Source recognition accuracy", y = "Photo recognition accuracy") +
  theme_bw()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  ggplot(aes(x = resp_source, y = resp_pic, color = cut_number(j_score, 5), fill = cut_number(j_score, 5))) + 
  geom_point(alpha = 0.1) + 
  geom_smooth( method = "lm", alpha = 0.2) + 
  labs(x = "Source recognition accuracy", y = "Photo recognition accuracy") +
  theme_bw()
```

@@

```{r}
retrieval %>% 
  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
  ggplot(aes(x = interest, y = acc_recall, color = j_score, fill = j_score)) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), alpha = 0.05) + 
  scale_color_viridis_c() +
  scale_fill_viridis_c() +
  labs(x = "Interest in fact at encoding", y = "Fact recall accuracy (generous)") +
  theme_bw()
```

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
  ggplot(aes(x = interest, y = acc_recall, color = cut_number(j_score, 4), fill = cut_number(j_score, 4))) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth( method = "glm", method.args = list(family = "binomial"), alpha = 0.2) + 
  labs(x = "Interest in fact at encoding", y = "Fact recall accuracy (generous)") +
  theme_bw()
```

@@

```{r}
retrieval %>% 
  # filter(already_knew == "none") %>% 
  ggplot(aes(x = interest, y = resp_pic, color = cut_number(j_score, 4), fill = cut_number(j_score, 4))) + 
  geom_point(alpha = 0.1) + 
  geom_smooth(method = "lm", alpha = 0.2) + 
  labs(x = "Interest in fact at encoding", y = "Photo recognition accuracy") +
  theme_bw()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  ggplot(aes(x = interest, y = resp_source, color = cut_number(j_score, 4), fill = cut_number(j_score, 4))) + 
  geom_point(alpha = 0.1) + 
  geom_smooth(method = "lm", alpha = 0.2) + 
  labs(x = "Interest in fact at encoding", y = "Source recognition accuracy") +
  theme_bw()
```

# STOP! Dirty graphs ahead

```{r}
retrieval %>% 
  ggplot(aes(x = log(rt_pic), y = resp_pic)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  facet_wrap(~subj_num, scales = "free_x")
```

```{r}
retrieval %>% 
  ggplot(aes(x = log(rt_source), y = resp_source)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  facet_wrap(~subj_num, scales = "free_x")
```

>>>>

```{r}
j_exp %>% 
  ggplot(aes(x = j_score)) +
  geom_histogram(binwidth = .05) +
  geom_vline(xintercept = 0.7, linetype = "dotted") +
  labs(x = "Expertise score")
```

@@

```{r}
j_exp %>% 
  mutate(subj_num = factor(subj_num)) %>% 
  left_join(q_google_demos, by = "subj_num") %>% 
  ggplot(aes(x = j_score, fill = gender)) +
  geom_histogram(binwidth = .05, position = "identity", alpha = 0.5) +
  geom_vline(xintercept = 0.7, linetype = "dotted") +
  labs(x = "Expertise score")
```

@@

```{r}
j_exp %>% 
  mutate(subj_num = factor(subj_num)) %>% 
  left_join(q_google_demos, by = "subj_num") %>% 
  ggplot(aes(x = age, y = j_score)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_hline(yintercept = 0.7, linetype = "dotted") +
  labs(y = "Expertise score")
```

@@

@@

```{r}
j_meta %>%
  filter(!is.na(resp)) %>% 
  left_join(j_recall %>% select(subj_num, answer, acc_recall)) %>% 
  filter(acc_recall) %>% 
  ggplot(aes(x = subj_num, fill = resp)) +
  geom_bar() +
  labs(x = "Participant", y = "# facts labeled with that memory state", fill = "Memory state") +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        legend.position = 0:1,
        legend.justification = 0:1,
        legend.background = element_blank())
```

@@

```{r}
j_meta %>%
  left_join(j_recall %>% select(subj_num, answer, acc_recall)) %>% 
  filter(acc_recall) %>% 
  count(subj_num, resp) %>% 
  group_by(subj_num) %>% 
  mutate(prob = n / sum(n)) %>% 
  ggplot(aes(x = subj_num, y = prob, fill = resp)) +
  geom_col() +
  labs(x = "Participant", y = "Percent facts labeled with that memory state", fill = "Memory state") +
  theme_bw() +
  theme(axis.text.x = element_blank())
```

@@

### How many people got which categories?

```{r}
encoding %>% 
  distinct(subj_num, group, category) %>% 
  mutate(category = fct_relevel(category, "arms", "gems", "musi")) %>% 
  ggplot(aes(x = category, fill = group)) +
  geom_bar() +
  theme(legend.position = 0:1, legend.justification = 0:1, legend.background = element_blank())
```

@@

### Are some categories more interesting than others?

```{r}
encoding %>% 
  group_by(group_trial_num, category) %>% 
  summarize(interest_mean = mean(resp), interest_sd = sd(resp)) %>% 
  ggplot(aes(x = interest_mean, fill = category)) +
  geom_density(alpha = 0.5) +
  labs(x = "Mean (across Ps) interest rating for each fact") +
  theme(legend.position = 0:1,
        legend.justification = 0:1,
        legend.background = element_blank(),
        legend.direction = "horizontal")
```

@@

### Are trivia experts more interested overall?

```{r}
encoding %>% 
  group_by(subj_num, j_score) %>% 
  summarize(resp = mean(resp)) %>% 
  ggplot(aes(x = j_score, y = resp)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score",
       y = "P's mean interest (across facts)")
```

@@

```{r}
encoding %>% 
  ggplot(aes(x = subj_num, fill = fct_rev(already_knew))) +
  geom_bar() +
  geom_hline(yintercept = 40, linetype = "dotted") +
  scale_x_discrete(guide = guide_axis(angle = 30)) +
  labs(x = "Participant (expertise low to high)", y = "# facts already knew", fill = "Prior knowledge") +
  theme_bw() +
  theme(axis.text.x = element_blank())
```

@@

```{r}
retrieval_temp <- retrieval %>% 
  nest(data = -subj_num) %>% 
  slice_sample(n = 8) %>% 
  unnest(data)

retrieval_temp %>% 
  ggplot(aes(x = retrieval_trial_num, y = acc_recall)) +
  geom_rect(aes(x = NULL, y = NULL, xmin = xmin, xmax = xmax, fill = retrieval_block_type),
            data = retrieval_temp %>%
              select(subj_num, retrieval_block, retrieval_trial_num, retrieval_block_type) %>%
              group_by(subj_num, retrieval_block) %>%
              filter(retrieval_trial_num %in% range(retrieval_trial_num)) %>%
              mutate(xtype = if_else(retrieval_trial_num == min(retrieval_trial_num), "xmin", "xmax")) %>%
              ungroup() %>%
              pivot_wider(names_from = xtype, values_from = retrieval_trial_num) %>% 
              mutate(xmin = xmin - 0.5,
                     xmax = xmax + 0.5),
            ymin = 0, ymax = 1, alpha = 0.5) +
  geom_line() +
  geom_point(aes(color = already_knew)) +
  # scale_colour_viridis_b() +
  scale_y_continuous(n.breaks = 3) +
  facet_grid(subj_num ~ .) +
  labs(x = "Fact recall trial (beginning to end)", y = "Fact recall accuracy", fill = "Chunk type") +
  theme_bw()
```

@@

### Is recall higher when people already know (some of) the facts?

```{r}
retrieval %>% 
  filter(!is.na(already_knew)) %>% 
  group_by(subj_num, already_knew) %>% 
  summarize(acc_recall = mean(acc_recall)) %>% 
  ggplot(aes(x = already_knew, y = acc_recall)) +
  geom_violin() +
  labs(x = "Fact prior knowledge at encoding", y = "% correct recall")
```

@@

A-A' 2AFC with similar lure

```{r}
r_pics %>%
  group_by(subj_num, j_score) %>% 
  mutate(acc = mean(resp)) %>% 
  ggplot(aes(x = j_score, y = acc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = " Mean accuracy with confidence")
```

@@

```{r}
r_source %>%
  group_by(subj_num, j_score) %>% 
  mutate(acc = mean(resp)) %>% 
  ggplot(aes(x = j_score, y = acc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = " Mean accuracy with confidence")
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
  ggplot(aes(x = resp_pic, y = acc_recall, color = cut_number(j_score, 3), fill = cut_number(j_score, 3))) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth( method = "glm", method.args = list(family = "binomial"), alpha = 0.2) + 
  labs(x = "Photo recognition accuracy",
       y = "Fact recall accuracy (generous)",
       color = "Expertise tertile",
       fill = "Expertise tertile") +
  theme(legend.position = c(0, 0.75),
        legend.justification = c(0, 0.75),
        legend.background = element_blank())
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         resp_pic = resp_pic / 100,
         j_score = j_score - 0.7) %>% 
  lme4::glmer(acc_recall ~ resp_pic * j_score + (1 + resp_pic | subj_num), data = ., family = "binomial") %>%
  summary()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
  ggplot(aes(x = resp_source,
             y = acc_recall,
             color = cut_number(j_score, 3),
             fill = cut_number(j_score, 3))) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth( method = "glm", method.args = list(family = "binomial"), alpha = 0.2) + 
  labs(x = "Source recognition accuracy",
       y = "Fact recall accuracy (generous)",
       color = "Expertise tertile",
       fill = "Expertise tertile") +
  theme(legend.position = c(0, 0.75),
        legend.justification = c(0, 0.75),
        legend.background = element_blank())
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         resp_source = resp_source / 100,
         j_score = j_score - 0.7) %>% 
  lme4::glmer(acc_recall ~ resp_source * j_score + (1 + resp_source | subj_num),
              data = ., family = "binomial") %>% 
  summary()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  ggplot(aes(x = resp_source, y = resp_pic, color = cut_number(j_score, 3), fill = cut_number(j_score, 3))) +
  geom_point(alpha = 0.1) + 
  geom_smooth( method = "lm", alpha = 0.2) + 
  labs(x = "Source recognition accuracy",
       y = "Photo recognition accuracy",
       color = "Expertise tertile",
       fill = "Expertise tertile") +
  theme(legend.position = c(0, 0.5),
        legend.justification = c(0, 0.5),
        legend.background = element_blank())
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(resp_pic = resp_pic / 100,
         resp_source = resp_source / 100,
         j_score = j_score - 0.7) %>% 
  lme4::lmer(resp_pic ~ resp_source * j_score + (1 + resp_source | subj_num),
              data = .) %>% 
  summary()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
  ggplot(aes(x = interest, y = acc_recall, color = cut_number(j_score, 3), fill = cut_number(j_score, 3))) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth( method = "glm", method.args = list(family = "binomial"), alpha = 0.2) + 
  labs(x = "Interest in fact at encoding",
       y = "Fact recall accuracy (generous)",
       color = "Expertise tertile",
       fill = "Expertise tertile") +
  theme(legend.position = c(0, 0.75),
        legend.justification = c(0, 0.75),
        legend.background = element_blank())
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  ggplot(aes(x = interest, y = resp_pic, color = cut_number(j_score, 3), fill = cut_number(j_score, 3))) + 
  geom_point(alpha = 0.1) + 
  geom_smooth(method = "lm", alpha = 0.2) + 
  labs(x = "Interest in fact at encoding",
       y = "Photo recognition accuracy",
       color = "Expertise tertile",
       fill = "Expertise tertile") +
  theme(legend.position = c(0, 0.5),
        legend.justification = c(0, 0.5),
        legend.background = element_blank())
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  ggplot(aes(x = interest, y = resp_source, color = cut_number(j_score, 3), fill = cut_number(j_score, 3))) + 
  geom_point(alpha = 0.1) + 
  geom_smooth(method = "lm", alpha = 0.2) + 
  labs(x = "Interest in fact at encoding",
       y = "Source recognition accuracy",
       color = "Expertise tertile",
       fill = "Expertise tertile") +
  theme(legend.position = c(0, 0.5),
        legend.justification = c(0, 0.5),
        legend.background = element_blank())
```
